Based on [doi.org/10.1073/pnas.07052901](https://doi-org.libproxy.utdallas.edu/10.1073/pnas.0705290104 "https://doi-org.libproxy.utdallas.edu/10.1073/pnas.0705290104")04, look at physical appearance looking for vs. self-perception and the effect of gender

Variables:

Time 1 (initial survey): gender, attr1_1 (preference), attr3_1 (opinion of own), attr5_1 (how think percieved)

Time 2 (halfway through): attr1_s (preference), attr3_s (opinion of own)

Time 3 (next day): attr7_2 (actual importance), attr1_2 (preference), attr3_2 (opinion of own), attr5_2 (how think percieved)

Time 4 (3-4 weeks after): attr1_3 (preference), attr7_3 (actual importance), attr3_3 (opinion of own), attr5_3 (how think percieved)

```{r}
library(tidyverse)
library(Hmisc)
```

```{r}
data_path <- "speed_dating_data.csv"
spd_dat <- read.csv(data_path)
spddat <- subset(spd_dat, select=c(iid, gender, attr1_1, attr3_1, attr5_1,
                                   attr1_s, attr3_s,
                                   attr7_2, attr1_2, attr3_2, attr5_2,
                                   attr1_3, attr7_3, attr3_3, attr5_3))
```

```{r}
s11 <- subset(spddat, select=c(attr1_1, attr3_1, attr5_1, 
                              attr3_s, attr3_2, attr5_2,
                              attr3_3, attr5_3))
#s1s <- subset(spddat, select=c(attr1_s, attr3_1, attr5_1, 
#                              attr3_s, attr3_2, attr5_2,
#                              attr3_3, attr5_3))
#s72 <- subset(spddat, select=c(attr7_2, attr3_1, attr5_1, 
#                              attr3_s, attr3_2, attr5_2,
#                              attr3_3, attr5_3))
#s12 <- subset(spddat, select=c(attr1_2, attr3_1, attr5_1, 
#                              attr3_s, attr3_2, attr5_2,
#                              attr3_3, attr5_3))
#s13 <- subset(spddat, select=c(attr1_3, attr3_1, attr5_1, 
#                              attr3_s, attr3_2, attr5_2,
#                              attr3_3, attr5_3))
#s73 <- subset(spddat, select=c(attr7_3, attr3_1, attr5_1, 
#                              attr3_s, attr3_2, attr5_2,
#                              attr3_3, attr5_3))
spddats <- list(s11)
```

```{r}
spddat.rcorr = rcorr(as.matrix(spddat))
spddat.coeff = spddat.rcorr$r
spddat.p = spddat.rcorr$P
```

```{r}
coeff = data.frame(spddat.coeff)
p = data.frame(spddat.p)

coeff <- subset(coeff, select=c(attr1_1, attr1_s, attr1_2, attr7_2, attr1_3, attr7_3))
coeff <- coeff[!(row.names(coeff) %in% c("gender", "attr1_1", "attr1_s", "attr1_2",
                                         "attr7_2", "attr1_3", "attr7_3")),]
p <- subset(p, select=c(attr1_1, attr1_s, attr1_2, attr7_2, attr1_3, attr7_3))
p <- p[!(row.names(p) %in% c("gender", "attr1_1", "attr1_s", "attr1_2", "attr7_2", 
                             "attr1_3", "attr7_3")),]
coeff
```

```{r}
p
```

```{r}
ggplot(coeff, aes(attr1_1, attr1_1))+
  geom_point() +
  ylim(c(-.1, 1))
ggplot(coeff, aes(attr1_s, attr1_s))+
  geom_point() +
  ylim(c(-.1, 1))
ggplot(coeff, aes(attr1_2, attr1_2))+
  geom_point() +
  ylim(c(-.1, 1))
ggplot(coeff, aes(attr7_2, attr7_2))+
  geom_point() +
  ylim(c(-.1, 1))
ggplot(coeff, aes(attr1_3, attr1_3))+
  geom_point() +
  ylim(c(-.1, 1))
ggplot(coeff, aes(attr7_3, attr7_3))+
  geom_point() +
  ylim(c(-.1, 1))
```

```{r}
spddat <- subset(spddat, select=c(iid, gender, attr1_1, attr3_1))
spddat <- na.omit(spddat)
spddat <- unique(spddat)
spddat %>% mutate(gender = recode(gender,
                                  '0' = "Women",
                                  '1' = "Men")) -> spddat
ggplot(spddat, aes(attr3_1, attr1_1, color=gender, group=gender)) +
  geom_point(position="jitter", alpha=0.5) +
  geom_smooth(method="gam", formula=y ~ s(x, bs = "cs", k=8)) +
  scale_colour_discrete(labels=c("Men", "Women"), type=c("#7b3494", "#008837")) +
  labs(title = "Physical attractiveness preference vs. self-perception",
       colour = "Gender") +
  xlab("Self-Rating") +
  ylab("Weight in Decision to Match (%)") +
  theme_light() +
  theme(text = element_text(family="Avenir"))
```

```{r}
ggplot(spddat, aes(attr3_1, attr1_1)) +
  geom_hex() +
  labs(title = "Physical attractiveness preference vs. self-perception") +
  xlab("Self-Rating") +
  ylab("Weight in Decision to Match (%)") +
  theme_light() +
  theme(text = element_text(family="Avenir"))
```

```{r}
ggplot(spddat, aes(attr3_1, attr1_1, color=gender)) +
  geom_density_2d() +
  labs(title = "Physical attractiveness preference vs. self-perception") +
  scale_colour_discrete(labels=c("Men", "Women"), type=c("#d01c8b", "#4dac26")) +
  scale_x_continuous(breaks=c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)) +
  labs(title = "Physical Attractiveness",
       subtitle = "Do participants' self-ratings impact their preferences?",
       colour = "Gender") +
  xlab("Self-Rating from 1-10") +
  ylab("Weight in Decision to Match (%)") +
  annotate("label", label="Pearson's r = 0.18, p < .001", x=5.5, y=40, family="Avenir") +
  theme_light() +
  theme(text = element_text(family="Avenir"))
```

```{r}
spddatw <- subset(spddat, gender == 0)
spddatm <- subset(spddat, gender == 1)
spddatw.rcorr = rcorr(as.matrix(spddatw))
spddatw.coeff = spddatw.rcorr$r
spddatw.p = spddatw.rcorr$P
spddatm.rcorr = rcorr(as.matrix(spddatm))
spddatm.coeff = spddatm.rcorr$r
spddatm.p = spddatm.rcorr$P
print(data.frame(spddatw.coeff))
print(data.frame(spddatw.p))
print(data.frame(spddatm.coeff))
print(data.frame(spddatm.p))
```
